weight_analyses

### 2023-04-04 smelt_2019_winterspring/Diet.Rmd

# bring in data
```{r}
diet <- read_csv("smelt_2019_winterspring/data_raw/2019_smeltstudy_diet_data.csv")
diet$Location <- ordered(diet$Location, levels = c("RVR", "DWSC"))
diet<-diet[diet$Cage.ID != "FCCL Control Tank 1",]
diet<-diet[diet$Cage.ID != "FCCL Control Tank 2",]
diet<-diet[diet$Cage.ID != "FCCL Control",]

@@

#bind fish measurements with stomach contents (note- some lost due to missing letters in ID's-update for final)
total <- merge(diet_type, Cage, by=c("Tag"))

#create instantaneous ration column
total$IR <- (total$Contents.Weight/total$Post_Weight_g)*100

@@

#sum for taxa abundance among individual fish
taxa_tag<- diet_type %>% 
  group_by(Location, Mesh, Cage.ID, Tag, Taxa, LH.Stage) %>% 
  summarize("count.sum"= sum(Count))

@@

#add rows for all taxa for all fish
full.prop<-stomach_abundance %>% complete(Tag, Taxa) %>%
  as.data.frame()

@@

#select columns I want for count
full.count<-subset(full.count, select=c("Location", "Mesh", "Tag", "Taxa", "LH.Stage", "count.sum"))

#select columns I want for proportion
full.prop.3<-subset(full.prop.2, select=c("Tag", "Taxa", "proportion", "Location", "Mesh"))
#replace proportion Nas with zeros
diet.prop<-full.prop.3 %>% replace_na(list(proportion=0))

#average across fish
diet.prop.mean<- diet.prop %>% 
  group_by(Taxa, Location, Mesh) %>% 
  summarize("prop.mean"= mean(proportion))
```

@@

taxa.perct<- diet_type %>% 
  group_by(Location, Taxa, Prey.Taxa) %>% 
  summarize("count.sum"= sum(Count, na.rm=TRUE))

@@

taxa.perct$percent <- (taxa.perct$count.sum/taxa.perct$Total)*100
```

>>>>

# bring in data
```{r}
diet <- read_csv("smelt_2019_winterspring/data_raw/2019_smeltstudy_diet_data.csv")
diet$Location <- ordered(diet$Location, levels = c("RVR", "DWSC"))
diet<-diet[diet$Cage != "FCCL Control Tank 1",]
diet<-diet[diet$Cage != "FCCL Control Tank 2",]
diet<-diet[diet$Cage != "FCCL Control",]
diet <- diet %>% rename(Cage.ID = Cage) # Cat: I added this because there was no Cage.ID before

@@

#bind fish measurements with stomach contents (note- some lost due to missing letters in ID's-update for final)
total <- merge(diet_type, Cage, by=c("Tag")) %>%
  filter(!is.na(Delta_CF))

#create instantaneous ration column
total$IR <- (total$ContentsWeight/total$Post_Weight_g)*100

@@

#sum for taxa abundance among individual fish
taxa_tag<- diet_type %>% 
  group_by(Location, Mesh, Cage.ID, Tag, TaxonomicGrouping, LHStage) %>% 
  summarize("count.sum"= sum(Count))

@@

#add rows for all taxa for all fish
full.prop<-stomach_abundance %>% complete(Tag, TaxonomicGrouping) %>%
  as.data.frame()

@@

#select columns I want for count
full.count<-subset(full.count, select=c("Location", "Mesh", "Tag", "TaxonomicGrouping", "LHStage", "count.sum"))

#select columns I want for proportion
full.prop.3<-subset(full.prop.2, select=c("Tag", "TaxonomicGrouping", "proportion", "Location", "Mesh"))
#replace proportion Nas with zeros
diet.prop<-full.prop.3 %>% replace_na(list(proportion=0))

#average across fish
diet.prop.mean<- diet.prop %>% 
  group_by(TaxonomicGrouping, Location, Mesh) %>% 
  summarize("prop.mean"= mean(proportion))
```

@@

taxa.perct<- diet_type %>% 
  group_by(Location, TaxonomicGrouping, PreyTaxa) %>% 
  summarize("count.sum"= sum(Count, na.rm=TRUE))

@@

taxa.perct$percent <- round((taxa.perct$count.sum/taxa.perct$Total)*100,2)

```

Write table for supplementary. 
```{r}
taxa_percent_table <- taxa.perct %>%
  dplyr::select(Site = Location,
         `Taxonomic Grouping` = TaxonomicGrouping,
         Taxa = PreyTaxa,
         `Sum Count` = count.sum,
         `Percent Count` = percent) %>%
  arrange(Site, desc(`Percent Count`))

write_csv(taxa_percent_table, "smelt_2019_winterspring/data_clean/diet_supp_table.csv")
```

### 2023-04-04 smelt_2019_winterspring/ZoopPlotting_Tow.Rmd

# bind throw and tow methods & calcualte species abundance for Table 6
```{r}
#combine
tow$radius<-tow$RingSize*2
abundance <- rbind(tow, throw)
abundance$Date<-ymd(abundance$Date)
abundance$Taxa<-as.factor(abundance$TaxonomicGrouping)
abundance$ind_m3<-as.numeric(abundance$ind_m3)

@@

dw$DWSC.Bio <- dw$bio
dw$DWSC.Perc <- (dw$DWSC.Bio/12832.26)*100
dw <- dw[c(2,3,6,7)]
dw2 <- subset(dw, DWSC.Bio!=0)

rv$RV.Bio <- rv$bio
rv$RV.Perc <- (rv$RV.Bio/32782.81)*100
rv <- rv[c(2,3,6,7)]
rv2 <- subset(rv, RV.Bio!=0)

@@

#change NA to 0  
all[is.na(all)] <- 0

write_excel_csv(all, "smelt_2019_winterspring/data_clean/species.table.csv")
```

@@

tiff(filename="smelt_2019_winterspring/figures/zoopfig.tiff", 
    units="in", 
    width=7.25, #or 3.5 for single column
    height=3.75, #height you can adjust according to your plot
    res=600, compression="lzw")
print(z)
dev.off()
```

@@

shapiro.test(for.mod$bio.all) #not significant

model<-lm(bio.all~Location*Week2, data=for.mod)
anova(model)

@@

leveneobject<- lm(abs(resid(model))~Location*Week2, data=for.mod)
anova(leveneobject) #insignificant

marginal = emmeans(model, 
                   ~ Location*Week2)

cld(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey") #DWSC and RV different
```

>>>>

# bind throw and tow methods & calcualte species abundance for Table 6
```{r}
#combine
tow$radius<-tow$RingSize*2
#abundance <- rbind(tow, throw)
abundance <- tow
abundance$Date<-ymd(abundance$Date)
abundance$Taxa<-as.factor(abundance$TaxonomicGrouping)
abundance$ind_m3<-as.numeric(abundance$ind_m3)
abundance$Location <- factor(abundance$Location, levels = c("RV", "DWSC"))

@@

dw$DWSC.Bio <- dw$bio
dw$DWSC.Perc <- (dw$DWSC.Bio/sum$sum[sum$Location=="DWSC"])*100
dw <- dw[c(2,3,6,7)]
dw2 <- subset(dw, DWSC.Bio!=0)

rv$RV.Bio <- rv$bio
rv$RV.Perc <- (rv$RV.Bio/sum$sum[sum$Location == "RV"])*100
rv <- rv[c(2,3,6,7)]
rv2 <- subset(rv, RV.Bio!=0)

@@

#change NA to 0  
all[is.na(all)] <- 0
all_write <- all %>%
  arrange(Taxon) %>%
  mutate(across(c(RV.Bio: DWSC.Perc), round, 1))

write_excel_csv(all_write, "smelt_2019_winterspring/data_clean/species.table_tow.csv")
```

@@

tiff(filename="smelt_2019_winterspring/figures/zoopfig_towonly.tiff", 
    units="in", 
    width=7.25, #or 3.5 for single column
    height=3.75, #height you can adjust according to your plot
    res=600, compression="lzw")
print(z)
dev.off()
```

@@

shapiro.test(for.mod$bio.all) # significant

model<-lm(bio.all~Location * Week2, data=for.mod)
anova(model)

@@

leveneobject<- lm(abs(resid(model))~Location + Week2, data=for.mod)
anova(leveneobject) #insignificant

marginal = emmeans(model, 
                   ~ Location* Week2)

cld(marginal,
    alpha   = 0.05, 
    Letters = letters,     
    adjust  = "tukey") #DWSC and RV different

emmip(model, Week2 ~ Location)
emtrends(model, pairwise ~ Location, var = "Week2")
emm <- emmeans(model, ~Location, type = "response")
emm
pairs(emm, adjust = "Week2")
```

```{r}
taxa %>%
  dplyr::select(Date, Location, Week) %>%
  distinct() %>%
  group_by(Location, Week) %>%
  summarize(n = n())
```
